---
title: "prjoect"
output: html_document
date: "2023-08-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, fig.width=11,fig.height=8}
  #remove cols
library(readxl)
library(dplyr)
library(survival)
library(survminer)
library(finalfit)
library(tidyverse)
library(psych)
library(survminer)
library(forestplot)
library(gtsummary)
library(dynpred)
library(googlesheets4)
googlesheets4::gs4_deauth()
df_desc <- read_sheet("https://docs.google.com/spreadsheets/d/1MF5z4SF0R6qGiZnuyWwb2W9dACdN_Bmzx0SIi-oLPjw/edit?usp=sharing", sheet = 1)

#df_desc <- read_excel("C:/Users/user/Downloads/DM2.xlsx")
df_desc <- df_desc %>%
  select(-1,-2,-23,-24,-26)

#rename vars
df_desc <- df_desc %>% 
  rename(aGVHD = `('Was GVHD diagnosis established?', 'Acute GVHD')`,
                    cGvHD = `('Was GVHD diagnosis established?', 'Chronic GVHD')`,
        aGVHD_date = `('GVHD diagnosis date', 'Acute GVHD')`,
        cGVHD_date = `('GVHD diagnosis date', 'Chronic GVHD')`, 
         aGVHD_grade = `Grade of acute GVHD`, 
         cGVHD_grade = `Grade of chronic GVHD`,  
         Dg = `Main Diagnosis`)
#add id var
df_desc <- rowid_to_column(df_desc, "id")

#change HH in cgvhd dates
df_desc[124, "cGVHD_date"] <- "15/09/2021"
df_desc[299, "cGVHD_date"] <- "15/07/2021"
df_desc[301, "cGVHD_date"] <- "15/06/2021"
#transform dates
df_desc <- df_desc %>%
  mutate(Birth = dmy(Birth),
         LCDTC = dmy(LCDTC),
         DEATHDTC = dmy(DEATHDTC),
         RELAPDTC = dmy(RELAPDTC),
         TRDTC = dmy(TRDTC),
         aGVHD_date = dmy(aGVHD_date),
         cGVHD_date = dmy(cGVHD_date)
         )
#calculate dates
df_desc <- df_desc %>%
  mutate(
FU_time = as.double(difftime(LCDTC, TRDTC)),
Death_time = as.double(difftime(DEATHDTC, TRDTC)),
Age_tr = (as.double(difftime( TRDTC, Birth, units = "days")))/365.25,
Relapse_time = as.double(difftime(RELAPDTC, TRDTC)),
aGVHD_time = as.double(difftime(aGVHD_date,TRDTC)),
cGVHD_time = as.double(difftime(cGVHD_date, TRDTC))
)

#remove date vars
df_desc <- df_desc %>%
  select(-Birth, - LCDTC, -DEATHDTC, - RELAPDTC, - TRDTC, - aGVHD_date, -cGVHD_date)
df_desc <- df_desc %>%
mutate (FU_time = ifelse(is.na(FU_time), Death_time, FU_time))

#Relapse
df_desc <- df_desc %>%
  mutate(compet_relapse = ifelse(RELAPYN == "no" | RELAPYN == "unknown", FU_time, Relapse_time),
         status_rel = ifelse(RELAPYN == "no" | RELAPYN == "unknown", PTSTAT, RELAPYN)
         )
#recode relapse
df_desc <- df_desc %>%
  mutate(status_rel = case_when(status_rel == "alive" ~ 0, 
                                status_rel == "died" ~ 1, 
                                status_rel == "yes" ~ 2))
#recode TR type
df_desc <- df_desc %>%
  mutate(TRTYPE = ifelse(TRTYPE == 2, 5, TRTYPE))
#Transform PTSTAT to numeric
df_desc <- df_desc %>%
  mutate(PTSTAT = ifelse(PTSTAT == "alive", 0, 1))

#recode cgvhd grade
df_desc <- df_desc %>%
  mutate(cGVHD_grade = ifelse(is.na(cGVHD_grade) | cGVHD_grade == "mild", "None or mild", cGVHD_grade))

# kaplan meyer
km_overall <- survfit(Surv(FU_time, PTSTAT) ~ 1, data=df_desc)
tbl_survfit(km_overall, times = c(1,100*(1:20)))

Overall_plot <- ggsurvplot(
   km_overall,                    # survfit object with calculated statistics.
   title = "OS",
   conf.int = TRUE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  risk.table.height=.15,
    # plot the number of censored subjects at time 
)



#create efs variable

df_desc <- df_desc %>%
  mutate(efs = ifelse(status_rel == 2, 1, status_rel))

```

## Общая выживаемость

### Общая 
```{r echo=FALSE, fig.width=11,fig.height=8}

LMdata <- dynpred::cutLM(df_desc, outcome = list(time ="FU_time", status = "PTSTAT"), LM = 0, horizon = 365.25*2, covs = list(fixed = c("SITE", "Sex",  "TRNUM", "RELAPYN", "TRTYPE", "TRSOURCE", "CONDTYPE", "aGVHD", "cGvHD", "aGVHD_grade", "cGVHD_grade", "GVGD_proph", "aGVHD_grade", "cGVHD_grade", "Dg", "GVGD_proph" ), format ="wide"))

#PLOT OS AT 2 years
km_LM <- survfit(Surv(FU_time, PTSTAT == 1) ~ 1, data=LMdata)
LM_plot <- ggsurvplot(
   km_LM,                    # survfit object with calculated statistics.
   title = "OS",
   conf.int = TRUE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
    # plot the number of censored subjects at time 
)

#subset for AL
 LMdataAL <- subset(LMdata, Dg == "Acute")
 
 
```

### По виду донора 
```{r echo=FALSE, fig.width=11,fig.height=8}

km_LM_donor <- survfit(Surv(FU_time, PTSTAT) ~ TRTYPE, data=LMdata)
LM_plot_donor <- ggsurvplot(
   km_LM_donor,                    # survfit object with calculated statistics.
   title = "OS",
   pval = TRUE, 
   conf.int = FALSE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  surv.median.line = "hv"
)

 
```

### По источнику трансплантата 
```{r echo=FALSE, fig.width=11,fig.height=8}


km_LM_source <- survfit(Surv(FU_time, PTSTAT) ~ TRSOURCE, data=LMdata)

LM_plot_source <- ggsurvplot(
   km_LM_source,                    # survfit object with calculated statistics.
   title = "OS",
   pval = TRUE, 
   conf.int = FALSE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.

  surv.median.line = "hv")
```

### По режиму кондиционирования
```{r echo=FALSE, fig.width=11,fig.height=8}

km_LM_cond <- survfit(Surv(FU_time, PTSTAT) ~ CONDTYPE, data=LMdata)

LM_plot_cond <- ggsurvplot(
   km_LM_cond,                    # survfit object with calculated statistics.
   title = "OS",
   pval = TRUE, 
   conf.int = FALSE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  surv.median.line = "hv")
 
```
## OS for AL

### Overall
```{r echo=FALSE, fig.width=11,fig.height=8}
km_LM_AL <- survfit(Surv(FU_time, PTSTAT == 1) ~ 1, data=LMdataAL)
LM_plot_AL <- ggsurvplot(km_LM_AL,                   
   title = "OS",
   conf.int = TRUE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.

    # plot the number of censored subjects at time 
)
```

### Donor type
```{r echo=FALSE, fig.width=11,fig.height=8}
km_LM_AL_donor <- survfit(Surv(FU_time, PTSTAT == 1) ~ TRTYPE, data=LMdataAL)
LM_plot_AL_donor <- ggsurvplot(km_LM_AL_donor, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )
```
### BMT source
```{r echo=FALSE, fig.width=11,fig.height=8}
km_LM_AL_source <- survfit(Surv(FU_time, PTSTAT == 1) ~ TRSOURCE, data=LMdataAL)
LM_plot_AL_source <- ggsurvplot(km_LM_AL_source, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "OS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )
```  

### Conditioning
```{r echo=FALSE, fig.width=11,fig.height=8}
km_LM_AL_cond <- survfit(Surv(FU_time, PTSTAT == 1) ~ CONDTYPE, data=LMdataAL)
LM_plot_AL_cond <- ggsurvplot(km_LM_AL_cond, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "OS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )
```
  
  
  
## Event-Free survival

### Overall EFS
```{r echo=FALSE, fig.width=11,fig.height=8}
# Event - relapse, death

#Data for relapse status at 500
LMdata_relapse <- dynpred::cutLM(df_desc, outcome = list(time ="compet_relapse", status = "efs"), LM = 0, horizon = 375.25*2, covs = list(fixed = c("SITE", "Sex",  "TRNUM", "TRTYPE", "TRSOURCE", "CONDTYPE", "aGVHD", "cGvHD", "aGVHD_grade", "cGVHD_grade", "GVGD_proph"), format ="wide"))



km_LM_relapse <- survfit(Surv(compet_relapse, efs) ~ 1, data=LMdata_relapse)
LM_plot_relapse <- ggsurvplot(km_LM_relapse, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "EFS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )

```
### EFS by donor
```{r echo=FALSE, fig.width=11,fig.height=8}
km_LM_relapse_donor <- survfit(Surv(compet_relapse, efs) ~ TRTYPE, data=LMdata_relapse)
LM_plot_relapse_donor <- ggsurvplot(km_LM_relapse_donor, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "EFS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )

```
### BMT source
```{r echo=FALSE, fig.width=11,fig.height=8}
  km_LM_relapse_source <- survfit(Surv(compet_relapse, efs) ~ TRSOURCE, data=LMdata_relapse)
LM_plot_relapse_source <- ggsurvplot(km_LM_relapse_source, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "EFS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )

```
### Conditioning
```{r echo=FALSE, fig.width=11,fig.height=8}
  km_LM_relapse_cond <- survfit(Surv(compet_relapse, efs) ~ CONDTYPE, data=LMdata_relapse)
LM_plot_relapse_cond <- ggsurvplot(km_LM_relapse_cond, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "EFS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  )

```
## Landmark for agvhd and cgvhd
```{r echo=FALSE, fig.width=11,fig.height=8}
#Landmark for agvhd OS
LM_agvhd <- dynpred::cutLM(df_desc, outcome = list(time ="FU_time", status = "PTSTAT"), LM = 125, horizon = 365.25*2, covs = list(fixed = c("SITE", "Sex",  "TRNUM", "RELAPYN", "TRTYPE", "TRSOURCE", "CONDTYPE", "aGVHD_grade", "cGVHD_grade", "Dg", "GVGD_proph", "efs", "compet_relapse"), format ="wide"))
LM_agvhd <- LM_agvhd %>%
  mutate(aGVHD_grade = ifelse(is.na(aGVHD_grade) | aGVHD_grade == 1 | aGVHD_grade == 2, 0, 1))
    #km for agvhd OS
km_LM_agvhd <- survfit(Surv(FU_time, PTSTAT) ~ aGVHD_grade, data=LM_agvhd)
LM_plot_agvhd <- ggsurvplot(km_LM_agvhd, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "OS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  risk.table.height=.15)

LM_tbl_agvhd <- tbl_survfit(km_LM_agvhd, times = c(125,(365.25/2),365.25*(1:2))) %>%
   gtsummary::add_n() %>%
  gtsummary::add_nevent() %>%
  add_p() %>%
  as_flex_table()

#km for agvhd efs
LM_agvhd_efs <- dynpred::cutLM(df_desc, outcome = list(time ="compet_relapse", status = "efs"), LM = 125, horizon = 365.25*2, covs = list(fixed = c("SITE", "Sex",  "TRNUM", "RELAPYN", "TRTYPE", "TRSOURCE", "CONDTYPE", "aGVHD_grade", "cGVHD_grade", "Dg", "GVGD_proph"), format ="wide"))
LM_agvhd_efs <- LM_agvhd_efs %>%
  mutate(aGVHD_grade = ifelse(is.na(aGVHD_grade) | aGVHD_grade == 1 | aGVHD_grade == 2, 0, 1))
km_LM_agvhd_efs <- survfit(Surv(compet_relapse, efs) ~ aGVHD_grade, data=LM_agvhd_efs)
LM_tbl_agvhd_efs <- tbl_survfit(km_LM_agvhd_efs, times = c(125,(365.25/2),365.25*(1:2))) %>%
   gtsummary::add_n() %>%
  gtsummary::add_nevent() %>%
  add_p() %>%
  as_flex_table()

LM_plot_agvhd_efs <- ggsurvplot(km_LM_agvhd_efs, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "EFS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  risk.table.height=.15)

#km for cgvhd OS
LM_cgvhd <- dynpred::cutLM(df_desc, outcome = list(time ="FU_time", status = "PTSTAT"), LM = 275, horizon = 365.25*2, covs = list(fixed = c("SITE", "Sex",  "TRNUM", "RELAPYN", "TRTYPE", "TRSOURCE", "CONDTYPE", "aGVHD_grade", "cGVHD_grade", "Dg", "GVGD_proph", "efs", "compet_relapse"), format ="wide"))

    #km for cgvhd OS
km_LM_cgvhd <- survfit(Surv(FU_time, PTSTAT) ~ cGVHD_grade, data=LM_cgvhd)
LM_plot_cgvhd <- ggsurvplot(km_LM_cgvhd, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "OS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  risk.table.height=.15)

LM_tbl_cgvhd <- tbl_survfit(km_LM_cgvhd, times = c(275,365.25*(1:2))) %>%
   gtsummary::add_n() %>%
  gtsummary::add_nevent() %>%
  add_p() %>%
  as_flex_table()

#km for cgvhd EFS
LM_cgvhd_efs <- dynpred::cutLM(df_desc, outcome = list(time ="compet_relapse", status = "efs"), LM = 275, horizon = 365.25*2, covs = list(fixed = c("SITE", "Sex",  "TRNUM", "RELAPYN", "TRTYPE", "TRSOURCE", "CONDTYPE", "aGVHD_grade", "cGVHD_grade", "Dg", "GVGD_proph", "efs", "compet_relapse"), format ="wide"))


    #km for cgvhd EFS
km_LM_cgvhd_efs <- survfit(Surv(compet_relapse, efs) ~ cGVHD_grade, data=LM_cgvhd_efs)
LM_plot_cgvhd_efs <- ggsurvplot(km_LM_cgvhd_efs, 
    pval = TRUE,                                   
   conf.int = FALSE,         # show confidence intervals for 
       title = "OS",                      # point estimaes of survival curves.
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 100,     # break X axis in time intervals by 200.
   risk.table = "absolute",  # absolute number and percentage at risk.
  risk.table.height=.15)

LM_tbl_cgvhd_efs <- tbl_survfit(km_LM_cgvhd_efs, times = c(275,365.25*(1:2))) %>%
   gtsummary::add_n() %>%
  gtsummary::add_nevent() %>%
  add_p() %>%
  as_flex_table()
```

## COX
###Univariate cox OS, time dependent AGVHD
```{r echo=FALSE, fig.width=11,fig.height=8}
#recode aGVHD grade
df_desc <- df_desc %>%
  mutate(aGVHD_grade = ifelse(is.na(aGVHD_grade) | aGVHD_grade == 1 | aGVHD_grade == 2, 0, 1))

#recode vars
df_desc <- df_desc %>%
  mutate(TRNUM = ifelse(TRNUM >=2, 2, 1))

df_desc <- df_desc %>%
  mutate(                        TRNUM = as.factor(TRNUM),
                        TRTYPE = as.factor(TRTYPE),
         TRSOURCE = as.factor(TRSOURCE),
         CONDTYPE = as.factor(CONDTYPE),
         aGVHD_grade = as.factor(aGVHD_grade))

#univ
explanatory = c("Sex", "Age_tr", "TRNUM", "TRTYPE", "TRSOURCE", "CONDTYPE", "Dg", "GVGD_proph")
dependent = "Surv(FU_time, PTSTAT)"
df_desc %>%
  coxphuni(dependent, explanatory) %>%
    fit2df -> uni_cox

#Tmerge
td_dat <- 
  tmerge(
    data1 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, FU_time, PTSTAT),
    data2 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, FU_time, PTSTAT, aGVHD_grade, aGVHD_time),
    id = id, 
    death = event(FU_time, PTSTAT),
    agvhd = tdc(aGVHD_time)
    )
#recode agvhd
td_dat <- td_dat %>%
  mutate(agvhd = as.factor(agvhd))

#agvhd uni cox 
coxph(Surv(tstart, tstop, death) ~ agvhd, data =td_dat) %>% fit2df -> agvhd_cox
#all uni cox
univ_cox <- rbind(uni_cox, agvhd_cox)
```
###multivariate cox OS, time dependent AGVHD
```{r echo=FALSE, fig.width=11,fig.height=8}
multi_os<-coxph(Surv(tstart, tstop, death) ~ agvhd + Sex + Age_tr + TRNUM + TRTYPE + TRSOURCE + CONDTYPE + Dg + GVGD_proph, data = td_dat, id = id)
forest_multi_os<-ggforest(multi_os, main = "aGVHD OS")
#assumptions
cox.zph(multi_os)
```
###multivariate and univariate cox OS, time dependent CGVHD
```{r echo=FALSE, fig.width=11,fig.height=8}
#Tmerge
td_dat2 <- 
  tmerge(
    data1 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, FU_time, PTSTAT, aGVHD_grade),
    data2 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, FU_time, PTSTAT, aGVHD_grade, cGvHD, cGVHD_time),
    id = id, 
    death = event(FU_time, PTSTAT),
    cgvhd = tdc(cGVHD_time)
    )

#recode vars
td_dat2 <- td_dat2 %>%
  mutate(cgvhd = as.factor(cgvhd))

#multi cox cgvhd
multi_os2<-coxph(Surv(tstart, tstop, death) ~ cgvhd + aGVHD_grade + Sex + Age_tr + TRNUM + TRTYPE + TRSOURCE + CONDTYPE + Dg + GVGD_proph, data = td_dat2, id = id)
forest_multi_os2<-ggforest(multi_os2, main = "cGVHD OS")
#assumptions
cox.zph(multi_os2)
```
## EFS uni
```{r echo=FALSE, fig.width=11,fig.height=8}
#univ
explanatory = c("Sex", "Age_tr", "TRNUM", "TRTYPE", "TRSOURCE", "CONDTYPE", "Dg", "GVGD_proph")
dependent = "Surv(compet_relapse, efs)"
df_desc %>%
  coxphuni(dependent, explanatory) %>%
    fit2df -> uni_cox_2

#Tmerge
td_dat_efs <- 
  tmerge(
    data1 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, compet_relapse, efs),
    data2 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, compet_relapse, efs,aGVHD_time,aGVHD_grade),
    id = id, 
    death = event(compet_relapse, efs),
    agvhd = tdc(aGVHD_time)
    )

#recode agvhd
td_dat_efs <- td_dat_efs %>%
  mutate(agvhd = as.factor(agvhd))

#agvhd uni cox 
coxph(Surv(tstart, tstop, death) ~ agvhd, data =td_dat_efs) %>% fit2df -> agvhd_cox_efs
#all uni cox
univ_cox_efs <- rbind(uni_cox_2, agvhd_cox_efs)
```
###multivariate cox efs, time dependent AGVHD
```{r echo=FALSE, fig.width=11,fig.height=8}
multi_efs<-coxph(Surv(tstart, tstop, death) ~ agvhd + Sex + Age_tr + TRNUM + TRTYPE + TRSOURCE + CONDTYPE + Dg + GVGD_proph, data = td_dat, id = id)
forest_multi_efs<-ggforest(multi_efs, main = "aGVHD EFS")
#assumptions
cox.zph(multi_efs)
```
###multivariate and univariate cox EFS, time dependent CGVHD
```{r echo=FALSE, fig.width=11,fig.height=8}
#Tmerge
td_dat_efs2 <- 
  tmerge(
    data1 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, compet_relapse, efs, aGVHD_grade),
    data2 = df_desc %>% select(id, Sex, Age_tr, TRNUM, TRTYPE, TRSOURCE, CONDTYPE, Dg, GVGD_proph, compet_relapse, efs, aGVHD_grade, cGvHD, cGVHD_time),
    id = id, 
    death = event(compet_relapse, efs),
    cgvhd = tdc(cGVHD_time)
    )

#recode vars
td_dat_efs2 <- td_dat_efs2 %>%
  mutate(cgvhd = as.factor(cgvhd))

#multi cox cgvhd
multi_efs2<-coxph(Surv(tstart, tstop, death) ~ cgvhd + aGVHD_grade + Sex + Age_tr + TRNUM + TRTYPE + TRSOURCE + CONDTYPE + Dg + GVGD_proph, data = td_dat2, id = id)
forest_multi_efs2<-ggforest(multi_efs2, main = "cGVHD EFS")
#assumptions
cox.zph(multi_efs2)
```


```{r echo=FALSE, fig.width=11,fig.height=9.5}
forest_multi_os
forest_multi_os2
forest_multi_efs
forest_multi_efs2

LM_plot
LM_plot_agvhd
LM_tbl_agvhd
LM_plot_agvhd_efs
LM_plot_cgvhd
LM_tbl_cgvhd
LM_plot_cgvhd_efs
LM_tbl_cgvhd_efs
LM_plot_cond
LM_plot_donor
LM_plot_source
LM_plot_relapse
LM_plot_relapse_cond
LM_plot_relapse_donor
LM_plot_relapse_source





